SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-21 paper.tex
add figure

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health with serious consequences.

>>>>

Fig.~\ref{intelligent-product} shows examples of embedded systems, which consist of a human-machine interface ({\it e.g.}, keyboard and LCD) and an instrumentation interface ({\it e.g.}, sensor, network, and actuator). Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health with serious consequences.
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{Embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}
